The Size Distribution of Firms and Industrial Water Pollution \\ A Quantitative Analysis of China

### 2019-09-23 Documentation/Pollution_Final_AEJ_Template_Ver2.tex
printing

\title{The Size Distribution of Firms and Industrial Water Pollution \\ A Quantitative Analysis of China}
\shortTitle{FIRM SIZE DISTRIBUTION AND POLLUTION}
\author{Ji Qi, Xin Tang, and Xican Xi\thanks{%
Qi: Chinese Academy for Environmental Planning, Room 709-B BeiKeChuangYe Tower, No.10 Dayangfang, Beiyuan Road, Beijing, China, 100012 (e-mail: qiji@caep.org.cn); Tang: Wuhan University and International Monetary Fund, 700 19th St NW, Washington D.C., United States, 20431 (e-mail:zjutangxin@gmail.com); Xi: School of Economics, Fudan University, 600 Guoquan Road, Shanghai, China, 200433 (e-mail:xicanxi@fudan.edu.cn). We are grateful for the comments from Alexis Anagnostoupolos, Marina Azzimonti, Juan Carlos Conesa, Berthold Herrendorf, Nicolai Kuminoff, Pietro Peretto, Edward Prescott, Diego Restuccia, Todd Schoellman, Kerry Smith, Daniel Yi Xu, Gustavo Ventura, the editor and three anonymous referees. We also benefited from the comments received at Arizona State University, the Chinese Academy of Environmental Planning, Duke University, the IMF, U.S International Trade Commission, Peking University, Shanghai University of Finance and Economics, Singapore Management University, Stony Brook University, Washington State University, Wuhan University, and Zhejiang University. We sincerely thank the China Ministry of Ecology and Environment for granting us access to the National General Survey of Pollution Sources data. This paper has been screened to ensure that no confidential data are revealed.}}
\date{\today}
\pubMonth{Month}
\pubYear{Year}
\pubVolume{Vol}
\pubIssue{Issue}
\JEL{E23, L11, O44, Q52, Q53, Q56}
\Keywords{Firm Size Distribution, Correlated Distortion, Industrial Water Pollution}

\begin{abstract}
    We argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China. Firm-level data indicate that larger firms are more likely to use clean technology but face higher distortions. In a heterogeneous firms model with an endogenous choice of pollution treatment technologies, we show that distortions that increase with firm-level TFP lower the adoption of clean technology, amplify aggregate pollution intensity, and lower aggregate output. Quantitatively, eliminating these correlated distortions would increase output by 30\% and decrease pollution by 20\%. Meanwhile, environmental regulations have sizable impact on pollution but only limited effect on output.
\end{abstract}

@@

Severe pollution has accompanied China's remarkable economic growth in the past few decades, causing environmental degradation, public health damage, and millions of premature deaths.\footnote{\citet{WorldBank_Cost_2007} estimates that the cost of air and water pollution in China is about 6\% of GDP. The health cost of pollution is estimated to be 4\% of GDP, the majority of which is associated with premature deaths caused by pollution. See \citet{Vennemoetal:2009} and \citet{ZhengKahn:2013} for review of empirical studies on environmental pollution in China.} Understanding the driving forces behind this severe pollution is crucial for designing and evaluating anti-pollution policies. An outstanding question is whether the severe pollution is an inevitable consequence of rapid economic growth, or largely exacerbated by policy distortions and/or market inefficiencies.

In this paper, we argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China. Using nationally representative data on firm production, pollution emissions and pollution treatment technologies, we document two facts on firm size and pollution intensity (pollutants per output) in China.\footnote{We use the \textit{National General Survey of Pollution Sources} (NGSPS) and \textit{National Economic Census} (CNEC) in China. Section I provides more details.} First, large firms have lower pollution intensity than small firms, with an elasticity of $-$0.37 between firm size and pollution intensity for the top five polluting industries in China.\footnote{The industries are ranked by their emissions of \textit{Chemical Oxygen Demand} (COD). The five industries are (with two-digit GB/T4547-2002 code in parentheses): Paper and Paper Products (C22), Processing of Food from Agricultural Products (C13), Textiles (C17), Raw Chemical Materials and Chemical Products (C26), and Beverages (C15).} Furthermore, we find that this is not only due to fewer pollutants per output are generated by large firms during production, but also that large firms are also more likely to use advanced end-of-pipe treatment technologies that require sizable fixed installation costs. Second, large firms account for a smaller proportion of the total employment in China than in the United States. For the top five polluting industries in China, firms with more than 400 employees account for 20\% of the total employment compared with close to 70\% for the U.S. counterparts. If we take the U.S. economy as a less distorted benchmark, these facts suggest that distortions to firm size distribution could have important environmental consequences in China.

Motivated by these facts, we build a two-sector (polluting and non-polluting) model of heterogeneous firms based on \citet{Lucas:1978b} to evaluate how firm-level distortions affect aggregate output and pollution. The model has the following key features. First, firms in each sector differ in their productivity levels. There is a stand-in household with a continuum of members, and each member draws a sector specific managerial ability from a given distribution. When members choose to be manager, they enter the sector their managerial ability belongs to and the ability determines the TFP of the firm they run. Second, firms differ in pollution intensity as well. As in \citet{CopelandTaylor:1994}, pollution emissions are a by-product of production for firms in the polluting sector. Following Fact 1 above, we assume that generated emissions per output during production is decreasing in firm output.\footnote{While our data reveal that large firms generate fewer pollutants per output, we do not know precisely the reasons behind that. Without further data, we model the emissions generated during production in a reduced-form way, which is then calibrated to the data. Section I.B discusses this point in more details.} Third, firms have the option to adopt an advanced end-of-pipe treatment technology, which we refer to as \textit{clean} technology later, after paying a fixed adoption cost. Firms in the polluting sector are subject to environmental regulations such that firms that do not use the clean technology face a penalty that takes away a fraction of their profits. As a result, our model predicts that only firms above a certain size threshold would choose the clean technology, which is qualitatively consistent with the fact that large firms are more likely to use clean technology.

@@

To discipline our quantitative analysis, we calibrate our model to match the observed pollution intensity, the adoption of clean technology, the correlation between distortions and firm TFP, and the firm size distribution in the Chinese data. We map the polluting sector to the top five polluting industries mentioned above, which account for 80\% of the total emissions in the data, and map the non-polluting sector to the rest of the manufacturing sector. We then use the calibrated model to evaluate the effects of two policies: removing correlated distortions from both sectors and strengthening environmental regulations.\footnote{Here we follow the so-called \textit{indirect} approach in the study of misallocation [\citet{RestucciaRogerson:2013}] by quantifying the overall effects of a variety of policies and institutions that relocate production factors from high to low TFP firms. Several examples of such policies include size-dependent taxes and subsidies, selective enforcement of regulations, financial constraints, poor enforcement of contracts, and internal trade costs, among others. This approach has been widely used in the misallocation literature, for instance, by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, \citet{AdamopoulosRestuccia:2014}, and \citet{BentoRestuccia:2016}, among others.}

Our quantitative results show that removing correlated distortions from both sectors would increase mean firm size by 130\% and aggregate output by 30\%, while lowering the pollution intensity of the polluting sector by 42\%. Since both sectors share similar distributions of firm TFP and distortions in the data, eliminating correlated distortions induces little reallocation across sectors. Therefore, aggregate pollution drops by 23\% because the technique effect dominates the scale effect. About half of the technique effect comes from the reallocation of factors across firms, while the rest is from a 27 percentage points increase in the adoption rate of clean technology. To isolate the importance of the \textit{progressivity} of distortions, we solve a version of the model in which the progressive taxes are replaced with flat taxes while holding the total tax revenue constant. Our results show that while the progressivity of distortions does not imply large output losses (7\%), it plays a central role in amplifying aggregate pollution (30\%).

In the second experiment, we increase the regulations to the extent that the fraction of firms adopting clean technology is the same as in the first experiment. We find that the policy reduces aggregate pollution by 14\%, but has very limited effect on aggregate output in the long run. Comparing this with the first experiment, we find that tightening environmental regulations {improves} the resource allocation on the \textit{extensive} margin of resource allocation by driving small unproductive firms out of the economy. However, the allocation {worsens} on the \textit{intensive} margin in the sense that among the remaining active firms, the production of medium-sized firms expands more at the expense of that of large firms. In contrast, the removal of correlated distortions improves the allocation on both margins.

@@

\textit{NGSPS.}---The NGSPS was a joint effort of multiple national ministries in China.\footnote{A more detailed description of the dataset can be found in Online Appendix A.} It covers all of the pollution units from the agricultural, industrial, and domestic sources, as well as facilities for the centralized treatment of pollution. In this study, we focus on the {industrial pollution sources}, which consist of businesses generating pollutants from the 39 manufacturing industries. The survey is organized directly by the State Council with data collection and quality control done by specially trained field staffs. According to the \textit{Regulation on the National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No. 508)]}, faking data would lead to financial penalties or even lawsuits. Therefore, the dataset is administrative in nature and is subject to less concerns of systematic under-reporting.\footnote{In fact, uniform under-reporting of emissions by small and large firms will not change the basic conclusions of this paper. Our results will be contaminated only if under-reporting by large firms is more severe than that by small firms, which is less likely in most polluting industries since larger firms are usually inspected more carefully. For instance, many large firms in these industries are identified as \textit{Key Pollution Sources}, and therefore are inspected and monitored by the government routinely and carefully, making it harder for them to fake data during this one-time survey.} While we are not aware of other economic studies that use NGSPS, a number of studies in environmental sciences have used this dataset.\footnote{See \citet{Niuetal:2016} and \citet{Qietal:2017} and the references therein for recent examples.}

The NGSPS collects information on the emissions of multiple air, water, and solid waste pollutants. In this paper, we focus on water pollution mainly because the data are more accurately measured than air pollution.\footnote{After our interview with the field staff, we learned that the differences in data quality was mainly caused by the differences in the sampling environment. For water pollution, firms rarely discharge wastewater directly. Instead, the wastewater is first stored in a sedimentation tank to settle heavier solids to the bottom and let lighter materials to float. This process creates a quiescent environment for sampling. For air pollutants, the sampling tube has to be placed in the chimneys, where the environment is much more volatile. Moreover, if firms were to manipulate their instant emissions when the field staff is on-site sampling, the sedimentation process makes it more difficult, since firms would have to clean the tank prior to the on-site visit of the field staff.} Among all the water pollutants, we focus on \textit{chemical oxygen demand} (COD), a major water pollutant that is commonly used to measure water quality. It measures the overall quantity of contaminants that will eventually cause oxygen loss and thus the death of living creatures. We choose COD because a much larger share of firms report positive emissions of COD compared to other pollutants. If we focus on other pollutants, such as hexavalent chromium, we would limit ourselves to a much smaller share of firms that engage in special production processes like leather tanning or pigment manufacturing.\footnote{See Table A.1 in Online Appendix A for the share of firms that report positive emissions for different water pollutants. We would like to stress that many firms do not report emissions of specific pollutants such as cyanidium or chromium simply because they do not use related materials in production. It is \textit{not} because of under-reporting or other issues related to data quality. In fact, since these pollutants are more hazardous than others, firms that discharge these pollutants are usually monitored more closely.} Moreover, COD emissions are typically highly correlated with the emissions of other pollutants when both are positive.\footnote{In the Paper and Paper Products industry, for example, the correlation between the emissions of COD and $\text{NH}_4^+$ is $\text{corr}(\text{COD},\text{NH}_4^+) = \text{0.82}$ and that between COD and BOD is $\text{corr}(\text{COD},\text{BOD}) = \text{0.94}$.}

The data reveal that industrial water pollutants are typically concentrated in a handful of industries, including COD. In our empirical analysis, we focus on the top five polluting industries in terms of COD emissions, which account for nearly 80\% of all COD emissions from industrial sources. Within narrowly defined manufacturing industries, the NGSPS divides firms into two large groups---\textit{key sources} and \textit{regular sources}. Firms identified as ``key sources'' are deemed as more polluting, and therefore are inspected and monitored by the government more carefully.\footnote{See Online Appendix A.1 for more information on the definition of key sources.} During this census, the field staff also collected extra information on these firms, and the data from these firms were inspected with greater care. Importantly, the key sources include both small and large firms, and the empirical densities of the log output of the key sources resemble the bell shape of those of all firms.\footnote{Please see Figure B.1 in Online Appendix B.} As a result, when empirically analyzing the relationship of firm size with pollution intensity and treatment technology adoption, we focus on the key sources, which account for more than 90\% of total COD emissions and 80\% of total output from the top five polluting industries (Table \ref{tab:top5summary}). The variables we use are the firm's output, the amount of major pollutants generated and emitted, installation costs of pollutant treatment technologies, industry (up to four-digit GB/T4574-2002), ownership classification, and province.

@@

\textit{CNEC.}---The CNEC was conducted by the National Bureau of Statistics in China. It was designed to cover {all} businesses that undertake economic activities in the secondary and tertiary industries in China. We use observations that belong to the manufacturing sector. The variables we use are the firm's output, labor compensation, book value of capital stock, number of employees, industry (up to four-digit GB/T4574-2002), ownership classification, and province.\footnote{A widely used firm-level dataset in China is the Annual Surveys of Industrial Firm (ASIF). We use CNEC instead of ASIF because that ASIF does not have information on non-state firms with sales below 5 million CNY, which are crucial for our analysis. If we used the 2004 ASIP, we would have missed 29\% of the employment and 80\% of the firms.}

@@

\textit{Firm Size and Pollution Intensity.---}To examine the statistical relationship between pollution intensity and firm size for the polluting sectors in China, we run the following regression using data on firms identified as ``key sources'' in the top five polluting industries:
\begin{equation}
    \log (\text{COD}_i) = \underset{(0.17)}{-3.75} + \underset{(0.01)}{0.63} \times \log (\text{Output}_i) + \vec{X} \vec{\gamma} + \varepsilon_i,
\label{eq:poolols}
\end{equation}
where $\vec{X} = \{\vec{X_s}, \vec{X_p}, \vec{X_o}\}$ refers to the dummy variables for two-digit industry, province, and ownership respectively. The estimates are all statistically significant at the 0.1\% level, with the standard errors reported in the parentheses below the estimates.

These estimates imply that as a firm's output increases by 1\%, its COD emissions would on average increase by only 0.63\%. We define pollution intensity as COD emissions per unit of output. Then the above estimates imply an elasticity of $-$0.37 between firm-level pollution intensity and output. That is, other things equal, a 1\% increase in firm output is associated with a 0.37\% decrease in pollution intensity. Figure \ref{fig:codscatter} visualizes this negative relationship, where the residuals from regressing intensity and output on the dummies are plotted to remove the influences of other covariates.\footnote{Recall that here by the \textit{Regression Anatomy Formula}, the slope of the least square fit in Figure \ref{fig:codscatter} is precisely one minus the coefficient on $\log(\text{Output})$ in Equation (\ref{eq:poolols}).} The estimation has an $R^2$ of 0.41, suggesting that nearly half of the variations in COD emissions can be explained by the variations in firm output and in the three sets of dummies.\footnote{We also tried other econometric specifications, and found similar negative correlations between pollution intensity and firm size. For instance, we estimated versions of Equation (\ref{eq:poolols}) for each industry and with robust standard errors clustered in provinces. Please see Online Appendix C for more information.} We would also like to point out that the coefficient of the dummy on whether a firm is state-owned or not, is statistically \textit{insignificant}. As a result, we do not distinguish between whether a firm is state-owned or not in our later analysis.

@@

To illustrate the difference in technology adoption by firms of different sizes, we use the Paper and Paper Products industry as an example.\footnote{We focus on one industry because of the potential heterogeneity in production processes across industries.} Table \ref{tab:techeffi} shows the mean abatement efficiency, median installation costs, and median output of firms that adopt these technologies, where the {abatement efficiency} is defined as one minus the ratio of {emitted COD} to {generated COD}.\footnote{Online Appendix D.2 provides more details.}
\begin{table}[t]
\footnotesize
\centering
\caption{Firm Size and Treatment Technologies}
\begin{tabular}{lcccc}
    \hline \hline
    Technology  & Mean Efficiency & Adoption Rate & Median Costs & Median Output \\
    \hline
    Physical    & 63.37\%         & 25.89\%       & 100                   & 100                       \\
    Chemical    & 74.96\%         & 33.64\%       & 308                   & 219                       \\
    Biological  & 80.90\%         & 38.60\%       & 923                   & 500                       \\
    \hline
\end{tabular}
\label{tab:techeffi}
\begin{tablenotes}[Source]
     NGSPS. 
\end{tablenotes}
\begin{tablenotes}
     The numbers reported are for the Paper and Paper Products (C22) industry. Abatement efficiency is defined as $1 - \text{COD Emitted}/\text{COD Generated}$. The median installation costs of physical technologies and median output of firms that adopt them are normalized to 100.
\end{tablenotes}
\end{table}
We find that for each 100 tons of COD generated, firms with biological technologies on average emit 19.1 tons of COD, compared to 36.6 tons for firms with physical technologies. Meanwhile, the median installation costs of biological technologies are 8 times higher than those of physical technologies. In addition, the median output of the firms using biological technologies are 4 times higher than those of firms with physical technologies. These point to increasing returns to scale in the adoption of cleaner technologies. As a result, small firms lack the profit margins needed to take advantage of these increasing returns to scale, while large firms are more likely to adopt cleaner technologies.

@@

Firms in the non-polluting sector solve the standard profit maximization problem:
\begin{equation*}
    \pi^c(z) = \max_{k,l} \left\{ (1-\tau_z) z^{1-\gamma}(k^{\alpha}l^{1-\alpha})^{\gamma} - Wl - Rk \right\},
\end{equation*}
where the superscript $c$ stands for ``clean.''

>>>>

\title{The Size Distribution of Firms and Industrial Water Pollution \\ A Quantitative Analysis of China}
\shortTitle{FIRM SIZE DISTRIBUTION AND POLLUTION}
\author{Ji Qi, Xin Tang, and Xican Xi\thanks{%
Qi: Chinese Academy for Environmental Planning, Room 709-B BeiKeChuangYe Tower, No.10 Dayangfang, Beiyuan Road, Beijing, China, 100012 (e-mail: qiji@caep.org.cn); Tang: Wuhan University and the International Monetary Fund, 700 19th St NW, Washington D.C., United States, 20431 (e-mail:zjutangxin@gmail.com); Xi: China Center for Economic Studies, School of Economics, Fudan University, 600 Guoquan Road, Shanghai, China, 200433, and  Shanghai Institute of International Finance and Economics (e-mail:xicanxi@fudan.edu.cn). We are grateful for the comments from Alexis Anagnostoupolos, Marina Azzimonti, Juan Carlos Conesa, Berthold Herrendorf, Nicolai Kuminoff, Pietro Peretto, Edward C. Prescott, Diego Restuccia, Todd Schoellman, V. Kerry Smith, Daniel Yi Xu, Gustavo Ventura, the editor and three anonymous referees. We also benefited from the comments received at Arizona State University, the Chinese Academy for Environmental Planning, Duke University, the International Monetary Fund, the U.S. International Trade Commission, Peking University, Shanghai University of Finance and Economics, Singapore Management University, Stony Brook University, Washington State University, Wuhan University, and Zhejiang University. We sincerely thank the China Ministry of Ecology and Environment for granting us access to the National General Survey of Pollution Sources data. This paper has been screened to ensure that no confidential data are revealed.}}
\date{\today}
\pubMonth{Month}
\pubYear{Year}
\pubVolume{Vol}
\pubIssue{Issue}
\JEL{E23, L11, O44, Q52, Q53, Q56}
\Keywords{Firm Size Distribution, Correlated Distortion, Industrial Water Pollution}

\begin{abstract}
    We argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China. Firm-level data indicate that larger firms are more likely to use clean technology but face higher distortions. In a heterogeneous firms model with an endogenous choice of pollution treatment technologies, we show that distortions that increase with firm-level TFP lower the adoption of clean technology, amplify aggregate pollution intensity, and lower aggregate output. Quantitatively, eliminating these correlated distortions would increase output by 30\% and decrease pollution by 20\%. Meanwhile, environmental regulations have sizable impact on pollution but limited effects on aggregate output.
\end{abstract}

@@

Severe pollution has accompanied China's remarkable economic growth in the past few decades, causing environmental degradation, public health damage, and millions of premature deaths.\footnote{\citet{WorldBank_Cost_2007} estimates that the total costs of air and water pollution in China are about 6\% of China's GDP. The health costs of pollution are estimated to be 4\% of GDP in China, the majority of which are associated with premature deaths caused by pollution. See \citet{Vennemoetal:2009} and \citet{ZhengKahn:2013} for reviews of empirical studies on pollution in China.} Understanding the driving forces behind this severe pollution is crucial for designing and evaluating anti-pollution policies. An outstanding question is whether the severe pollution is an inevitable consequence of rapid economic growth, or largely exacerbated by policy distortions and/or market inefficiencies.

In this paper, we argue that misallocation across firms amplifies industrial water pollution by distorting the firm size distribution in China. Using nationally representative data on firm production, pollution emissions and pollution treatment technologies, we document two facts on firm size and pollution intensity (pollutants per output) in China. %\footnote{We use the \textit{National General Survey of Pollution Sources} (NGSPS) and \textit{National Economic Census} (CNEC) in China. Section I provides more details.}
First, large firms have lower pollution intensity than small firms, with an elasticity of $-$0.37 between firm size and pollution intensity for the top five polluting industries in China. %\footnote{The industries are ranked by their emissions of \textit{Chemical Oxygen Demand} (COD). The five industries are (with two-digit GB/T4547-2002 code in parentheses): Paper and Paper Products (C22), Processing of Food from Agricultural Products (C13), Textiles (C17), Raw Chemical Materials and Chemical Products (C26), and Beverages (C15).}  Furthermore, we find that this is not only due to fewer pollutants per output are generated by large firms during production, but also that large firms are also more likely to use advanced end-of-pipe treatment technologies that require sizable fixed installation costs.
Not only do large firms generate  fewer pollutants per output during production, but they are also more likely to use advanced end-of-pipe treatment technologies that require large installation costs. Second, large firms account for a smaller proportion of the total employment in China than in the United States. For the top five polluting industries in China, firms with more than 400 employees account for 20\% of the total employment compared with close to 70\% for the U.S. counterparts. If we take the U.S. economy as a less distorted benchmark, these facts suggest that distortions to firm size distribution could have important environmental consequences in China.

Motivated by these facts, we build a two-sector (polluting and non-polluting) model of heterogeneous firms based on \citet{Lucas:1978b} to evaluate how firm-level distortions affect aggregate output and pollution. The model has the following key features. First, firms in each sector differ in their productivity levels. There is a stand-in household with a continuum of members, and each member draws a sector specific managerial ability from a given distribution. When members choose to be manager, they enter the sector their managerial ability belongs to and the ability determines the TFP of the firm they run. Second, firms differ in pollution intensity as well. As in \citet{CopelandTaylor:1994}, pollution emissions are a by-product of production for firms in the polluting sector. Following Fact 1 above, we assume that generated emissions per output during production is decreasing in firm output. %\footnote{While our data reveal that large firms generate fewer pollutants per output, we do not know precisely the reasons behind that. Without further data, we model the emissions generated during production in a reduced-form way, which is then calibrated to the data. Section I.B discusses this point in more details.}
Third, firms have the option to adopt an advanced end-of-pipe treatment technology, which we refer to as clean technology later, after paying a fixed adoption cost. Firms in the polluting sector are subject to environmental regulations such that firms that do not use the clean technology face a penalty that takes away a fraction of their profits. As a result, our model predicts that only firms above a certain size threshold would choose the clean technology, which is qualitatively consistent with the fact that large firms are more likely to use clean technology.

@@

To discipline our quantitative analysis, we calibrate our model to match the observed pollution intensity, the adoption of clean technology, the correlation between distortions and firm TFP, and the firm size distribution in the Chinese data. We map the polluting sector to the top five polluting industries mentioned above, which account for 80\% of the total emissions in the data, and map the non-polluting sector to the rest of the manufacturing sector. We then use the calibrated model to evaluate the effects of two policies: removing correlated distortions from both sectors and strengthening environmental regulations.%\footnote{Here we follow the so-called \textit{indirect} approach in the study of misallocation [\citet{RestucciaRogerson:2013}] by quantifying the overall effects of a variety of policies and institutions that relocate production factors from high to low TFP firms. Several examples of such policies include size-dependent taxes and subsidies, selective enforcement of regulations, financial constraints, poor enforcement of contracts, and internal trade costs, among others. This approach has been widely used in the misallocation literature, for instance, by \citet{HsiehKlenow:2009, HsiehKlenow:2014}, \citet{Bartelsmanetal:2013}, \citet{AdamopoulosRestuccia:2014}, and \citet{BentoRestuccia:2016}, among others.}

Our quantitative results show that removing correlated distortions from both sectors would increase mean firm size by 130\% and aggregate output by 30\%, while lowering the pollution intensity of the polluting sector by 42\%. Since both sectors share similar distributions of firm TFP and distortions in the data, eliminating correlated distortions induces little reallocation across sectors. Therefore, aggregate pollution drops by 23\% because the technique effect dominates the scale effect. About half of the technique effect comes from the reallocation of factors across firms, while the rest is from a 27 percentage points increase in the adoption rate of clean technology. To isolate the importance of the progressivity of distortions, we solve a version of the model in which the progressive taxes are replaced with flat taxes while holding the total tax revenue constant. Our results show that while the progressivity of distortions does not imply large output losses, it plays a central role in amplifying aggregate pollution: replacing the progressive taxes with flat taxes would cause a 7\% increase in aggregate output, and a 30\% decrease in aggregate pollution.

In the second experiment, we increase the regulations to the extent that the fraction of firms adopting clean technology is the same as in the first experiment. We find that the policy reduces aggregate pollution by 14\%, but has very limited effect on aggregate output in the long run. Comparing this with the first experiment, we find that tightening environmental regulations improves the resource allocation on the extensive margin of resource allocation by driving small unproductive firms out of the economy. However, the allocation {worsens} on the intensive margin in the sense that among the remaining active firms, the production of medium-sized firms expands more at the expense of that of large firms. In contrast, the removal of correlated distortions improves the allocation on both margins.

@@

\textit{NGSPS.}---The NGSPS was a joint effort of multiple national ministries in China. %\footnote{A more detailed description of the dataset can be found in Online Appendix A.}
It covers all of the pollution units from the agricultural, industrial, and domestic sources, as well as facilities for the centralized treatment of pollution. In this study, we focus on the {industrial pollution sources}, which consist of businesses generating pollutants from the 39 manufacturing industries. The survey is organized directly by the State Council with data collection and quality control done by specially trained field staffs. According to the \textit{Regulation on the National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No. 508)]}, faking data would lead to financial penalties or even lawsuits. Therefore, the dataset is administrative in nature and is subject to less concerns of systematic under-reporting.\footnote{In fact, uniform under-reporting of emissions by small and large firms will not change the basic conclusions of this paper. Our results will be contaminated only if under-reporting by large firms is more severe than that by small firms, which is less likely in most polluting industries since larger firms are usually inspected more carefully. For instance, many large firms in these industries are identified as \textit{key sources}, and therefore are inspected and monitored by the government routinely and carefully, making it harder for them to fake data during this one-time survey.} While we are not aware of other economic studies that use NGSPS, a number of studies in environmental sciences have used this dataset. See, for example, \citet{Niuetal:2016}, \citet{Qietal:2017} and the references therein. A more detailed description of the dataset can be found in Online Appendix A. %\footnote{See \citet{Niuetal:2016} and \citet{Qietal:2017} and the references therein for recent examples.}

The NGSPS collects information on the emissions of multiple air, water, and solid waste pollutants. In this paper, we focus on water pollution mainly because the data are more accurately measured than air pollution.\footnote{After our interview with the field staff, we learned that the differences in data quality was mainly caused by the differences in the sampling environment. For water pollution, firms rarely discharge wastewater directly. Instead, the wastewater is first stored in a sedimentation tank to settle heavier solids to the bottom and let lighter materials to float. This process creates a quiescent environment for sampling. For air pollutants, the sampling tube has to be placed in the chimneys, where the environment is much more volatile. Moreover, if firms were to manipulate their instant emissions when the field staff is on-site sampling, the sedimentation process makes it more difficult, since firms would have to clean the tank prior to the on-site visit of the field staff.} Among all the water pollutants, we focus on \textit{chemical oxygen demand} (COD), a major water pollutant that is commonly used to measure water quality. It measures the overall quantity of contaminants that will eventually cause oxygen loss and thus the death of living creatures. We choose COD because a much larger share of firms report positive emissions of COD compared to other pollutants. If we focus on other pollutants, such as hexavalent chromium, we would limit ourselves to a much smaller share of firms that engage in special production processes like leather tanning or pigment manufacturing.\footnote{See Table A.1 in Online Appendix A for the share of firms that report positive emissions for different water pollutants. We would like to stress that many firms do not report emissions of specific pollutants such as cyanidium or chromium simply because they do not use related materials in production. It is not because of under-reporting or other issues related to data quality. In fact, since these pollutants are more hazardous than others, firms that discharge these pollutants are usually monitored more closely.} Moreover, COD emissions are typically highly correlated with the emissions of other pollutants when both are positive.\footnote{In the Paper and Paper Products industry, for example, the correlation between the emissions of COD and $\text{NH}_4^+$ is $\text{corr}(\text{COD},\text{NH}_4^+) = \text{0.82}$ and that between COD and BOD is $\text{corr}(\text{COD},\text{BOD}) = \text{0.94}$.}

The data reveal that industrial water pollutants are typically concentrated in a handful of industries, including COD. In our empirical analysis, we focus on the top five polluting industries in terms of COD emissions, which account for nearly 80\% of all COD emissions from industrial sources. Within narrowly defined manufacturing industries, the NGSPS divides firms into two large groups---\textit{key sources} and \textit{regular sources}. Firms identified as key sources are deemed as more polluting, and therefore are inspected and monitored by the government more carefully. %\footnote{See Online Appendix A.1 for more information on the key sources.}
During this census, the field staff also collected extra information on these firms, and the data from these firms were inspected with greater care. Importantly, the key sources include both small and large firms, and the empirical densities of the log output of the key sources resemble the bell shape of those of all firms.\footnote{Please see Online Appendix A.1 for the formal definition of the key sources, and Figure B.1 in Online Appendix B for  the empirical densities of the log output of the key sources.} As a result, when empirically analyzing the relationship of firm size with pollution intensity and treatment technology adoption, we focus on the key sources, which account for more than 90\% of total COD emissions and 80\% of total output from the top five polluting industries (Table \ref{tab:top5summary}). The variables we use are the firm's output, the amount of major pollutants generated and emitted, installation costs of pollutant treatment technologies, industry (up to four-digit GB/T4574-2002), ownership classification, and province.

@@

\textit{CNEC.}---The CNEC was conducted by the National Bureau of Statistics in China. It was designed to cover {all} businesses that undertake economic activities in the secondary and tertiary industries in China. We use observations that belong to the manufacturing sector. The variables we use are the firm's output, labor compensation, book value of capital stock, number of employees, industry (up to four-digit GB/T4574-2002), ownership classification, and province.\footnote{A widely used firm-level dataset in China is the Annual Surveys of Industrial Firms (ASIF). We use CNEC instead of ASIF because that ASIF does not have information on non-state firms with sales below 5 million CNY, which are crucial for our analysis. If we used the 2004 ASIP, we would have missed 29\% of the employment and 80\% of the firms.}

@@

\textit{Firm Size and Pollution Intensity.---}To examine the statistical relationship between pollution intensity and firm size for the polluting sectors in China, we run the following regression using data on firms identified as key sources in the top five polluting industries:
\begin{equation}
    \log (\text{COD}_i) = \underset{(0.17)}{-3.75} + \underset{(0.01)}{0.63} \times \log (\text{Output}_i) + \vec{X} \vec{\gamma} + \varepsilon_i,
\label{eq:poolols}
\end{equation}
where $\vec{X} = \{\vec{X_s}, \vec{X_p}, \vec{X_o}\}$ refers to the dummy variables for two-digit industry, province, and ownership respectively. The estimates are all statistically significant at the 0.1\% level, with the standard errors reported in the parentheses below the estimates.

These estimates imply that as a firm's output increases by 1\%, its COD emissions would on average increase by only 0.63\%. We define pollution intensity as COD emissions per unit of output. Then the above estimates imply an elasticity of $-$0.37 between firm-level pollution intensity and output. That is, other things equal, a 1\% increase in firm output is associated with a 0.37\% decrease in pollution intensity. Figure \ref{fig:codscatter} visualizes this negative relationship, where the residuals from regressing intensity and output on the dummies are plotted to remove the influences of other covariates. %\footnote{Recall that here by the \textit{Regression Anatomy Formula}, the slope of the least square fit in Figure \ref{fig:codscatter} is precisely one minus the coefficient on $\log(\text{Output})$ in Equation (\ref{eq:poolols}).}
The estimation has an $R^2$ of 0.41, suggesting that nearly half of the variations in COD emissions can be explained by the variations in firm output and in the three sets of dummies.\footnote{We also tried other econometric specifications, and found similar negative correlations between pollution intensity and firm size. For instance, we estimated versions of Equation (\ref{eq:poolols}) for each industry and with robust standard errors clustered in provinces. Please see Online Appendix C for more information.} We would also like to point out that the coefficient of the dummy on whether a firm is state-owned or not, is statistically insignificant. As a result, we do not distinguish between whether a firm is state-owned or not in our later analysis.

@@

To illustrate the difference in technology adoption by firms of different sizes, we use the Paper and Paper Products industry as an example. By focusing on one specific industry, we abstract from the potential heterogeneity in production processes across industries. %\footnote{We focus on one industry because of the potential heterogeneity in production processes across industries.}
Table \ref{tab:techeffi} shows the mean abatement efficiency, median installation costs, and median output of firms that adopt these technologies, where the {abatement efficiency} is defined as one minus the ratio of {emitted COD} to {generated COD}. %\footnote{Online Appendix D.2 provides more details.}
\begin{table}[t]
\footnotesize
\centering
\caption{Firm Size and Treatment Technologies}
\begin{tabular}{lcccc}
    \hline \hline
    Technology  & Mean Efficiency & Adoption Rate & Median Costs & Median Output \\
    \hline
    Physical    & 63.37\%         & 25.89\%       & 100                   & 100                       \\
    Chemical    & 74.96\%         & 33.64\%       & 308                   & 219                       \\
    Biological  & 80.90\%         & 38.60\%       & 923                   & 500                       \\
    \hline
\end{tabular}
\label{tab:techeffi}
\begin{tablenotes}[Source]
     NGSPS.
\end{tablenotes}
\begin{tablenotes}
     The numbers reported are for the Paper and Paper Products (C22) industry. Abatement efficiency is defined as $1 - \text{COD Emitted}/\text{COD Generated}$. The median installation costs of physical technologies and median output of firms that adopt them are normalized to 100.
\end{tablenotes}
\end{table}
We find that for each 100 tons of COD generated, firms with biological technologies on average emit 19.1 tons of COD, compared to 36.6 tons for firms with physical technologies. Meanwhile, the median installation costs of biological technologies are 8 times higher than those of physical technologies. In addition, the median output of the firms using biological technologies are 4 times higher than those of firms with physical technologies. These point to increasing returns to scale in the adoption of cleaner technologies. As a result, small firms lack the profit margins needed to take advantage of these increasing returns to scale, while large firms are more likely to adopt cleaner technologies.

@@

Firms in the non-polluting sector solve the standard profit maximization problem:
\begin{equation*}
    \pi^c(z) = \max_{k,l} \left\{ (1-\tau_z) z^{1-\gamma}(k^{\alpha}l^{1-\alpha})^{\gamma} - Wl - Rk \right\},
\end{equation*}
where the superscript $c$ refers to the non-polluting sector.
